---
title: "p8105_hw6_ps3070"
output: github_document
---
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(knitr)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, out.width = "90%")

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

### Problem 1


```{r load & clean, message=FALSE, warning=FALSE}
birthweight = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>% 
  mutate(babysex = recode(babysex, "1" = "male", "2" = "female"),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         malform = recode(malform, "0" = "absent", "1" = "present"),
         babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         frace = relevel(frace, "White"),
         mrace = relevel(frace, "White"),
         malform = as.factor(malform)
         )
```

```{r missing, message=FALSE, warning=FALSE}
birthweight %>% 
  map_df(~sum(is.na(.)))
```
There is no missing data in the dataset.

### Regression model

The outcome is continuous, so I will use a linear regression model.

```{r linear model, message=FALSE, warning=FALSE}
bwt_base = lm(bwt ~ babysex + gaweeks + blength + mheight + smoken, data = birthweight) #linear model

bwt_model = modelr::add_residuals(birthweight, bwt_base) #residuals
bwt_model = modelr::add_predictions(bwt_model, bwt_base)

bwt_model %>%
  ggplot(aes(x = pred, y = resid, color = resid)) +
  geom_point(alpha = 0.5)
```

### Comparing model to two others

**Model 1: One using length at birth and gestational age as predictors (main effects only)**

```{r model 1, message=FALSE, warning=FALSE}
bwt1 =
  lm(bwt ~ blength + gaweeks, data = birthweight)
```

#### Model 2: One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r model 2, message=FALSE, warning=FALSE}
bwt2 =
  lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + blength*blength*babysex, data = birthweight)
```

